---
name: Alexander
surname: Severinsen
position: "Machine Learning Engineer"
address: "Øvre Gunnaråsen 21, 3475 Sætre"
phone: +47 993 77455
email: "alexander.severinsen@gmail.com"
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::moderncv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Om meg

 * 49 år, gift med Linda, 3 barn 
 * Løper, ski, jakt og fluefiske
 * Opptatt av miljø og bærekraft
 * Jobber for det meste i `R` og `SQL`, men om jeg må også `Python`. 
 * Maskinlæring, automatisering av rapporter og webapplikasjoner som plattform for analyse


# Arbeidserfaring

```{r}
library(tibble)
tribble(
  ~Year, ~Type, ~Desc,
  "2022-", "Machine Learning Engineer. Måling og verifikasjon av energitiltak. Modellutvikling", "Aneo AS",
  "2020-2022", "Machine Learning Engineer. Ansvar for videreutvikling av energiovervåkningsystemer (EOS), inkl. sanntidsovervåking", "Trønderenergi Kraft AS",
  "2016-2020", "Med-grunnlegger / Data scientist. Tech lead for utvikling av EOS med prognosebasert overvåkning av energibruk. Løsningen er i bruk for mer enn 2000 næringsbygg", "Storekeeper AS. Selskapet ble solgt til TrønderEnergi Kraft i 2020", 
  "2011-2016", "Rådgiver / Data scientist. Innleid i ulike data science prosjekter i Elkjøp, Telenor Mobil, Canal Digital, Inge Steensland", "Severinsen AS",
  "2010-2011", "Førsteamanuensis i markedsføring", "Handelshøgskolen, UiT Norges arktiske universitet",
  "2007-2010", "Senior CRM analytiker. Ansvarlig for å utvikle prognosemodeller vha. maskinlæring", "Telenor SA",
  "2003-2007", "Stipendiat, markedsføring", "Handelshøgskolen, UiT Norges arktiske universitet",
  "2000-2004", "Markedsanalytiker. Ansvarlig for å dokumentere effekten av generisk markedsføring i Spania og Japan", "Compario AS"
) %>% 
  brief_entries(
    glue::glue("{Type}"),
    Year, 
    Desc
  )
```

# Utdanning

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Topic, ~ Year, ~ Institution,
  "Industriell PhD", "Increased sustainability in the food retail sector through Measurement and Verification of energy conservation measures", "2018-2023", "Norges miljø- og biovitenskapelige universitet, Ås", 
  "Research fellow", "Økonometri, markedsføring og forbrukermodellering", "2003", "Massey University, Palmerston North, New Zealand",
  "Master",  "Spørreundersøkelser på Internett - design og implementering av surveys",  "1994-2000", "Norge fiskerihøgskole, Tromsø", 
) %>% 
  detailed_entries(Degree, Year, Topic, Institution)
# The QMSS Summer school
```

# Publikasjoner

-    Severinsen, Alexander, and Øystein Myrland. 2022. *ShinyRBase: Near real-time energy saving models using reactive programming*. Applied Energy, Volume 325, 119798. https://doi.org/10.1016/j.apenergy.2022.119798

-    Severinsen, Alexander, and Øystein Myrland. 2022. *Statistical learning to estimate energy savings from retrofitting in the Norwegian food retail market*. Renewable and Sustainable Energy Reviews, Volume 167, 112691. https://doi.org/10.1016/j.rser.2022.112691. 

-    Severinsen, Alexander, and Rob J. Hyndman. 2019. *Quantification of Energy Savings from Energy Conservation Measures in Buildings Using Machine Learning*. In ECEEE Summer Study Proceedings, 757--66. https://research.monash.edu/en/publications/quantification-of-energy-savings-from-energy-conservation-measure

-    Severinsen, Alexander, and Helen Marita Holst Sørensen. 2022. *A 3-step framework to benchmark potential and actual energy savings in retrofitting projects*. Currently under review in Sustainable Cities and Society. https://papers.ssrn.com/sol3/papers.cfm?abstract_id=4181531

-    Fagerström, Jonathan, Kari Aamodt Espegren, Josefine Selj, and Alexander Severinsen. 2019. [*Forecasting and Technoeconomic Optimization of PV-Battery Systems for Commercial Buildings*](https://www.eceee.org/library/conference_proceedings/eceee_Summer_Studies/2019/5-smart-and-sustainable-communities/forecasting-and-technoeconomic-optimization-of-pv-battery-systems-for-commercial-buildings/). In ECEEE Summer Study Proceedings, 949--54. 

- Lind, A., J. Selj, J. A. Tsanakas, P. Arnestad, and A. Severinsen. 2017. [*Shaving the Peaks through Statistical Learning: Smart Use of Solar Energy and Storage Solutions*](https://www.eceee.org/library/conference_proceedings/eceee_Summer_Studies/2017/5-buildings-and-construction-technologies-and-systems/shaving-the-peaks-through-statistical-learning-smart-use-of-solar-energy-and-storage-solutions/). In ECEEE Summer Study Proceedings, 1177–84.

- Severinsen, Alexander, and Helen Marita Holst. 2017. [*Using Machine Learning and Mathematical Programming to Benchmark Energy Efficiency of Buildings*](https://www.eceee.org/library/conference_proceedings/eceee_Summer_Studies/2017/5-buildings-and-construction-technologies-and-systems/using-machine-learning-and-mathematical-programming-to-benchmark-energy-efficiency-of-buildings/). In ECEEE-Summer Study Proceedings, 1083-1089


# Presentasjoner

- "Quantification of Energy Savings from Energy Conservation Measures in Buildings Using Machine Learning". ECEEE 2019 Summer Study on energy efficiency. June 7. https://paperpile.com/shared/m2NqR1

- "Lastprognoser - et 60 sekunders glimt". Horisont 2020. 20 Mars 2019. Det Norske Teater. https://www.youtube.com/watch?v=30pkeJ3Ajow&t=297s

– "Completely Missing Subject? Handling Missing Data in the Social Sciences". QMSS Conference. June 20-23. 2007. Prague. https://paperpile.com/shared/EsSmdi

- "Cognitive Models as Indicators of Success: Measuring the Effect of Generic Advertising". Johan Arndt Markedsføringskonferanse. 25-27 April 2007. https://paperpile.com/shared/hy5aD7

- "Balancing Aggresive and Defensive Marketing Strategies Using Efficient Time as a Benchmark". Johan Arndt Markedsføringskonferanse. 25-27 April 2007. https://paperpile.com/shared/cXXehC

- "The Choice Between Originality, or Replicating Old Work? A Case Study of How to Improve Confidence through Statistical Simulation". 18 July 2006. Research Methods Festival. Oxford. https://paperpile.com/shared/Wb9dz6

- "The Joint Effect of Promotion in Multiple Media - Exceeding the Level of Profitable Communication". December 1-6. ANZMAC. Brisbane. https://paperpile.com/shared/q0Q8GG






 
